### 2020-04-14 survival.tex
mostly figures

We use reliability censoring concepts to use information from units
that were proactively removed before failing as well as those still in
operation till the end. We use the R package {\tt survival} for the KM
analysis.
\begin{figure}
  \centering
  \includegraphics[width=6in]{figs/km_cage-node_o001.pdf}
  \caption{Survival probability from Kaplan-Meier analysis for {\tt
      old} batch GPUs, stratified by {\tt cage} and {\tt node}.}
  \label{fig:km-old-cage-node}
\end{figure}
\begin{figure}
  \centering
  \includegraphics[width=6in]{figs/km_cage-node_c001.pdf}
  \caption{Here we consider the effect of cage on survival among the
    old batch.}
  \label{fig:km-all-cage-node}
\end{figure}

@@

Both loc and move are roughly the same, indicating that GPUs that were
moved to another location had slighly (.75x) lower failure rate. This
may just reflect a “repair effect” that extends the life of a GPU. It
may have been removed and reinstalled for a reason that was not
recorded.

Oddly, the older batch has a very slighly lower hazard, although there
is a lot of uncertainty here, indicating that something more
complicated is at work and needs deeper investigation.

@@

It is strange that move and loc effects are opposite, whereas in the
univariate analysis they were the same. They are also much
stronger. The batch effect is opposite of what it was under univariate
analysys and a bit stronger as well. This is a concern and it may be
related to violation of the “proportionality assumption” of hazards
not crossing. We see some crossing in the survival curves above
already.

@@

\begin{figure}
  \includegraphics[width=5in]{figs/glmnet001.pdf}
  \caption{GPU variable importance from glmnet penalized regression analysis.}
\end{figure}

>>>>

We use reliability censoring concepts to use information from units
that were proactively removed before failing as well as those still in
operation till the end. We use the R package {\tt survival} for the KM
analysis.
\begin{figure}
  \centering
  \includegraphics[width=6in]{figs/km_cage-node_o001.pdf}
  \caption{Survival probability from Kaplan-Meier analysis for {\tt
      old} batch GPUs, stratified by {\tt cage} and {\tt node}.}
  \label{fig:km-old-cage-node}
\end{figure}
\begin{figure}
  \centering
  \includegraphics[width=6in]{figs/km_cage-node_c001.pdf}
  \caption{Comparison of the old and new batches, focusing only on
    three years of operation of the new batch so far.}
  \label{fig:km-all-cage-node}
\end{figure}

@@

@@

@@
